|

### 2021-02-08 appendix/appendix.Rmd
add text analysis exp01

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "estimatr", "kableExtra",
              "janitor", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

table_mm(amces, capt = "Average Marginal Component Effects -- Full Model")
```

@@

In this subsection, we test whether our results vary according to individual
characteristics, such as gender, age, race, income, support for death penalty,
and the respondents' opinions on the judicial system and the police forces. All
models report marginal means.

@@

@@

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "exp02main",
          title = "Experiment 02 -- Main Results", style = "apsr",
          dep.var.labels = "Lynching Support",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
```
\normalsize

@@

\footnotesize
```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02_group <- df_exp02 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
         education %in% c("College", "Graduate School", "Primary School",
                          "Secondary School", "High School")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education)),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School")) %>%
  mutate(views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad")) %>%
  mutate(views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good", 
                                    "Bad", "Very Bad")) %>%
  mutate(ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know",
                                "Rather Not Say")) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_),
  household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
                                  "Above R$5,000"))

@@

# Tables (robust standard errors from estimatr)
stargazer(m1, m2, m3, m4, m5, se = starprep(m1, m2, m3, m4, m5),
          p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
          header = FALSE, align = TRUE, label = "exp02demo1",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "Lynching Support",
          covariate.labels = c("Male", "Age (years)", "Black", "Mixed race",
                               "Asian", "Indigenous", "High school", "College",
                               "Graduate school", "3,001 to 5,000 BRL",
                               "5,000+ BRL"), style = "apsr",
          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female; 
                                              Model 3: White; Model 4: Primary or secondary school;",
                                              "Model 5: Up to 3,000 BRL. Robust standard errors in
                                              parentheses."),
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")

stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
          p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "exp02demo2",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "Lynching Support", style = "apsr",
          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right")
          column.sep.width = "2pt", notes = "Robust standard error in parentheses.",
          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
```
\normalsize

>>>>

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "estimatr", "grf", "kableExtra", "janitor",
              "quanteda", "seededlda", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

table_mm(amces, capt = "Average Marginal Component Effects -- Full Model")
```
\normalsize

@@

In this subsection, we test whether our results vary according to individual
characteristics, such as gender, age, race, income, support for death penalty,
and the respondents' opinions on the judicial system and the police forces. All
models report marginal means. As we shall see, the results are very robust
across all model specifications.

@@

## Text Analysis

In addition to the conjoint experiments, we also asked respondents to justify
their profile choices. We added a textbook after each conjoint and informed
subjects that their responses were optional. However, we obtained `r (nrow(df1) - sum(is.na(df1$q13_text))) + (nrow(df1) - sum(is.na(df1$q14_text))) + (nrow(df1) - sum(is.na(df1$q15_text))) + (nrow(df1) - sum(is.na(df1$q16_text))) + (nrow(df1) - sum(is.na(df1$q17_text)))` responses
in our survey, which we analyze here.

First, we concatenate all text responses into a single vector. Then we tokenize
the sentences, remove Portuguese stop words and punctuation, and select the
words that appear most frequently in the texts.

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence our previous findings and confirm that
respondents select lynching victim profiles according to these two factors.
Criminal characteristics, such as age or race, do not seem to be particularly
relevant, as respondents do not mention them as much. The next words are
_nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
(have to), and _justiça_ (justice). We believe these words correspond to cases
where respondents wanted to affirm they do not have any preference regarding
the lynching profiles, or that they would rather not have chosen any of the
alternatives.

\footnotesize
```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles"}
dfmat <- df1 %>%
  select(q13_text, q14_text, q15_text, q16_text, q17_text) %>%
  gather() %>%
  drop_na() %>%
  corpus(text_field = "value") %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE,
         remove_symbol = TRUE) %>%
  dfm() %>%
  dfm_remove(., pattern = c(stopwords("pt", source = "snowball"),
                            "é", "ser"))

# Plot
dfmat %>%
  textstat_frequency(n = 15) %>%
  ggplot(aes(x = reorder(feature, frequency), y = frequency)) +
  geom_point(colour = "#152238") +
  coord_flip() +
  labs(x = NULL, y = "Frequency") +
  theme_minimal()
```
\normalsize

We also construct a feature co-occurrence matrix (FCM) that shows which words
appear together in the responses we collected. Again, the results confirm the
findings of the conjoint experiment. As suggested in the previous graph, we see
a central cluster that describe crime and victim characteristics and includes
the words _linchamentos_ (lynchings), _caso_ (case), _estupro_ (rape),
_criança_ (child), _assassinato_ (murder), and _vítima_ (victim). This
highlights that these are the most important reasons why respondents choose
lynching profiles.

We also note that there is another word cluster on the left. It contains words
that indicate that some respondents do not support lynchings, such as _não_
(no), _opção_ (choice), _nada_ (nothing), _justifica_ (justifies),
_justificável_ (justifiable), and _escolher_ (choose).

\footnotesize
```{r conjoint-fcm, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Semantic network analysis"}
fcmat <- fcm(dfmat)
feat <- names(topfeatures(fcmat, 70))
fcmat_select <- fcm_select(fcmat, pattern = feat, selection = "keep")
size <- log(colSums(dfm_select(dfmat, feat, selection = "keep")))

# Plot
set.seed(144)
textplot_network(fcmat_select, min_freq = 0.8, vertex_size = size / max(size) * 3, max.overlaps = 30)
```
\normalsize

Lastly, we estimate a latent Dirichlet allocation (LDA) model to identify the
three most important topics in our corpus. The first topic includes words that
describes lynching perpetrators, as it contains the words like _polícia_
(police), _pessoas_ (people), and _família_ (family). The second topic
identifies the same words we associate with respondents who are against
lynchings, such as _nenhum_ (none), _opção_ (choice), _não_ (no), and _contra_
(against). The last topic, in contrast, refer to victim and crime
characteristics, which have also appeared in our previous estimations. Some of
the most common words in this group are _crime_ (crime), _criança_ (child),
_estupro_ (rape), _vítima_ (victim), _porque_ (because), _idoso_ (elderly),
_grave_ (serious), and _molestar_ (molest).

As our results show, respondents decide which individual deserves punishment
based on factors related to the crime he/she committed, specially the crime
victim. There is also a group of respondents that oppose lynchings in
principle, who affirm that lynchings are not justified.

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Latent Dirichlet allocation
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
```
\normalsize

@@

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02main",
          title = "Experiment 02 -- Main Results", style = "apsr",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
```
\normalsize

@@

\footnotesize
```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02_group <- df_exp02 %>%
  filter(gender %in% c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
         education %in% c("College", "Graduate School", "Primary School",
                          "Secondary School", "High School")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education)),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School")) %>%
  mutate(views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad")) %>%
  mutate(views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad")) %>%
  mutate(ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know",
                                "Rather Not Say")) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_),
  household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
                                  "Above R$5,000"))

@@

# Tables (robust standard errors from estimatr)
stargazer(m1, m2, m3, m4, m5, se = starprep(m1, m2, m3, m4, m5),
          p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02demo1",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
          column.labels = c("Gender", "Age", "Race", "Education", "Income"),
          covariate.labels = c("Male", "Years", "Black", "Mixed Race",
                               "Asian", "Indigenous", "High School", "College",
                               "Graduate School", "3,001 to 5,000 BRL", "5,000+ BRL"),
          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female;
                                              Model 3: White; Model 4: Primary or secondary school;",
                                              "Model 5: Up to 3,000 BRL. Robust standard errors in
                                              parentheses."),
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")

```
\clearpage

```{r exp02-demographics2, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
          p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp02demo2",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
          column.labels = c("Ideology", "Previous Victimization", "Police",
                            "Judiciary"),
          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right",
                               "Don't Know", "Rather Not Say", "Yes",
                               "Very Good", "Good", "Bad", "Very Bad",
                               "Don't Know", "Rather Not Say",
                               "Very Good", "Good", "Bad", "Very Bad",
                               "Don't Know", "Rather Not Say"),
          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Center;
                                              Model 2: No; Model 3: Regular; Model 4: Regular.",
                                              "Robust standard errors in parentheses."),
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
```
\normalsize

\footnotesize
```{r exp02-forest, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6, eval=F}
df_exp02_police <- df_exp02_group %>%
  select(exp02_outcomes, exp02_police_treat, gender, age, race, education, household_income2, ideology, views_police, views_justice) %>%
  mutate(exp02_police_treat = as.numeric(exp02_police_treat))

  drop_na()

library(FindIt)
F1 <-FindIt(model.treat = exp02_outcomes ~ exp02_police_treat,
            model.main = ~ race,
            model.int = ~ race,
            data = df_exp02_police,
            type = "binary",
            treat.type = "single")

F1 <-FindIt(model.treat= outcome ~ treat,
            model.main= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75,
            model.int= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75, data = LaLonde, type="binary", treat.type="single")

cases <- sample(seq_len(nrow(df_exp02_police)), round(nrow(df_exp02_police) * .6))
train <- df_exp02_police[cases, ]
test <- df_exp02_police[-cases, ]

x <- c("age")
g <- c("gender", "race", "education", "household_income2",
"ideology", "views_police", "views_justice")
X2 <- model.matrix(~ 0 + ., train[c(x, g)])

cf <- causal_forest(
  X = X2,
  Y = as.numeric(train$exp02_outcomes),
  W = as.integer(train$exp02_police_treat),
  num.trees = 1000,
  seed = 1839
)

cf %>%
  variable_importance() %>%
  as.data.frame() %>%
  mutate(variable = colnames(cf$X.orig)) %>%
  arrange(desc(V1))

preds <- predict(
  object = cf,
  newdata = model.matrix(~ ., data = test[, 3:ncol(train)]),
  estimate.variance = TRUE
)

test$preds <- preds$predictions

ggplot(test, aes(x = views_justice, y = preds)) +
  geom_point() +
  geom_smooth(method = "loess", span = 1) +
  theme_light()

average_treatment_effect(cf, target.sample = "all")
tree <- get_tree(cf, 1)
plot(tree)

dr_scores <- double_robust_scores(cf)
tree <- policy_tree(X2, dr_scores, 3)
plot(tree)
plot_htes(preds, ci = TRUE)
```
